Moral Foundations of U.S. Political News Organizations

### 2019-04-07 pilot_manuscript.Rmd
all updates! WOOO

nozero = subset(master_kav, wordcount > 0)
tapply(nozero$wordcount, nozero$Source, mean)
tapply(nozero$wordcount, nozero$Source, sum)

@@

nozero = subset(master_gs, wordcount > 0)
tapply(nozero$wordcount, nozero$Source, mean)
tapply(nozero$wordcount, nozero$Source, sum)

@@

```{r descriptives_both, include = FALSE}
##summarize the dataset so that you have the total and percent for each foundation
#kav
summary(harm_final_data_kav)
summary(fair_final_data_kav)
summary(ingroup_final_data_kav)
summary(authority_final_data_kav)
summary(purity_final_data_kav)
#gs
summary(harm_final_data_gs)
summary(fair_final_data_gs)
summary(ingroup_final_data_gs)
summary(authority_final_data_gs)
summary(purity_final_data_gs)
##report descriptive statistics of the foundations
#kav
mean(harm_final_data_kav$valence)
sd(harm_final_data_kav$valence)
mean(fair_final_data_kav$valence)
sd(fair_final_data_kav$valence)
mean(ingroup_final_data_kav$valence)
sd(ingroup_final_data_kav$valence)
mean(authority_final_data_kav$valence)
sd(authority_final_data_kav$valence)
mean(purity_final_data_kav$valence)
sd(purity_final_data_kav$valence)
#gs
mean(harm_final_data_gs$valence)
sd(harm_final_data_gs$valence)
mean(fair_final_data_gs$valence)
sd(fair_final_data_gs$valence)
mean(ingroup_final_data_gs$valence)
sd(ingroup_final_data_gs$valence)
mean(authority_final_data_gs$valence)
sd(authority_final_data_gs$valence)
mean(purity_final_data_gs$valence)
sd(purity_final_data_gs$valence)
#note that a big problem is the valence of the words 
```

@@

harm_final_temp_kav$Source[grepl("nytimes.com", harm_final_temp_kav$URL)] = "NY Times"
harm_final_temp_kav$Source[grepl("npr.org", harm_final_temp_kav$URL)] = "NPR"
harm_final_temp_kav$Source[grepl("slate.com", harm_final_temp_kav$URL)] = "Slate"
harm_final_temp_kav$Source[grepl("huffingtonpost.com", harm_final_temp_kav$URL)] = "Huffington Post"
harm_final_temp_kav$Source[grepl("politico.com", harm_final_temp_kav$URL)] = "Politico"
harm_final_temp_kav$Source[grepl("foxnews.com", harm_final_temp_kav$URL)] = "Fox"
harm_final_temp_kav$Source[grepl("breitbart.com", harm_final_temp_kav$URL)] = "Breitbart"
harm_final_temp_kav$Source[grepl("rushlimbaugh.com", harm_final_temp_kav$URL)] = "Rush Limbaugh"
harm_final_temp_kav$Source[grepl("theblaze.com", harm_final_temp_kav$URL)] = "The Blaze"
harm_final_temp_kav$Source[grepl("hannity.com", harm_final_temp_kav$URL)] = "Sean Hannity"
harm_model_kav = lme(MFDweight ~ lean, 
                 data = harm_final_temp_kav, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(harm_model_kav)
```

@@

purity_final_temp_gs$Source[grepl("nytimes.com", purity_final_temp_gs$URL)] = "NY Times"
purity_final_temp_gs$Source[grepl("npr.org", purity_final_temp_gs$URL)] = "NPR"
purity_final_temp_gs$Source[grepl("slate.com", purity_final_temp_gs$URL)] = "Slate"
purity_final_temp_gs$Source[grepl("huffingtonpost.com", purity_final_temp_gs$URL)] = "Huffington Post"
purity_final_temp_gs$Source[grepl("politico.com", purity_final_temp_gs$URL)] = "Politico"
purity_final_temp_gs$Source[grepl("foxnews.com", purity_final_temp_gs$URL)] = "Fox"
purity_final_temp_gs$Source[grepl("breitbart.com", purity_final_temp_gs$URL)] = "Breitbart"
purity_final_temp_gs$Source[grepl("rushlimbaugh.com", purity_final_temp_gs$URL)] = "Rush Limbaugh"
purity_final_temp_gs$Source[grepl("theblaze.com", purity_final_temp_gs$URL)] = "The Blaze"
purity_final_temp_gs$Source[grepl("hannity.com", purity_final_temp_gs$URL)] = "Sean Hannity"
purity_model_gs = lme(MFDweight ~ lean, 
                 data = purity_final_temp_gs, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(purity_model_gs)
```
# Experiment 2

@@

```{r exp2 source descriptives_both, results = 'asis', echo = FALSE, message = F}
#Kav
final_kav$uniquewords = NA
final_kav$valenceavg = NA

@@

#change this to match
apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
          caption = "Kavanaugh - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 6))
          )

#GS
final_gs$uniquewords = NA
final_gs$valenceavg = NA

@@

#calculate d
#harm
harm_d_kav = d.ind.t(m1 = mean(harm_final_temp_kav$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
                 sd1 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
                 sd2 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
                 n1 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"]),
                 n2 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"]),
                 a = .05)

@@

#put in the numbers
tableprint_kav[1, ] = c("Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1, 
                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                    harm_d_kav$d)
tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1, 
                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
                    fair_d_kav$d)
tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1, 
                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
                    ingroup_d_kav$d)
tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1, 
                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
                    authority_d_kav$d)
tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1, 
                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
                    purity_d_kav$d)

@@

#calculate d
#harm
harm_d_gs = d.ind.t(m1 = mean(harm_final_temp_gs$MFDweight[harm_final_temp$lean == "Conservative"], na.rm = T), 
                 m2 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
                 sd1 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
                 sd2 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
                 n1 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"]),
                 n2 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"]),
                 a = .05)

@@

#put in the numbers
tableprint_gs[1, ] = c("Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1, 
                    summary(harm_model)$tTable[2,4], summary(harm_model)$tTable[2,5],
                    harm_d_gs$d)
tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1, 
                    summary(fair_model)$tTable[2,4], summary(fair_model)$tTable[2,5],
                    fair_d_gs$d)
tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1, 
                    summary(ingroup_model)$tTable[2,4], summary(ingroup_model)$tTable[2,5],
                    ingroup_d_gs$d)
tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1, 
                    summary(authority_model)$tTable[2,4], summary(authority_model)$tTable[2,5],
                    authority_d_gs$d)
tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1, 
                    summary(purity_model)$tTable[2,4], summary(purity_model)$tTable[2,5],
                    purity_d_gs$d)

@@

tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
     height = 3, units = 'in', compression = "lzw")
plot(graph_data_kav)
dev.off()
```

>>>>

nozero = subset(master_kav, wordcount > 0)
nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")
tapply(nozero$wordcount, nozero$Source, mean)
tapply(nozero$wordcount, nozero$Source, sum)

@@

nozero = subset(master_gs, wordcount > 0)
nozero = subset(nozero, Source == "NY Times" | Source == "BLAZE" | Source == "NPR" | Source == "HUFFPO" | Source == "FOX" | Source == "HANNITY" | Source == "SLATE" | Source == "POLITICO" | Source == "RUSH" | Source == "BREITBART")

tapply(nozero$wordcount, nozero$Source, mean)
tapply(nozero$wordcount, nozero$Source, sum)

@@

```{r descriptives_both, include = FALSE}
##summarize the dataset so that you have the total and percent for each foundation
#kav
summary(harm_final_data_kav)
summary(fair_final_data_kav)
summary(ingroup_final_data_kav)
summary(authority_final_data_kav)
summary(purity_final_data_kav)
#gs
summary(harm_final_data_gs)
summary(fair_final_data_gs)
summary(ingroup_final_data_gs)
summary(authority_final_data_gs)
summary(purity_final_data_gs)
##report descriptive statistics of the foundations
#kav
mean(harm_final_data_kav$valence, na.rm = T)
sd(harm_final_data_kav$valence, na.rm = T)
mean(fair_final_data_kav$valence, na.rm = T)
sd(fair_final_data_kav$valence, na.rm = T)
mean(ingroup_final_data_kav$valence, na.rm = T)
sd(ingroup_final_data_kav$valence, na.rm = T)
mean(authority_final_data_kav$valence, na.rm = T)
sd(authority_final_data_kav$valence, na.rm = T)
mean(purity_final_data_kav$valence, na.rm = T)
sd(purity_final_data_kav$valence, na.rm = T)
#gs
mean(harm_final_data_gs$valence, na.rm = T)
sd(harm_final_data_gs$valence, na.rm = T)
mean(fair_final_data_gs$valence, na.rm = T)
sd(fair_final_data_gs$valence, na.rm = T)
mean(ingroup_final_data_gs$valence, na.rm = T)
sd(ingroup_final_data_gs$valence, na.rm = T)
mean(authority_final_data_gs$valence, na.rm = T)
sd(authority_final_data_gs$valence, na.rm = T)
mean(purity_final_data_gs$valence, na.rm = T)
sd(purity_final_data_gs$valence, na.rm = T)
#note that a big problem is the valence of the words 
```

@@

harm_final_temp_kav$Source[grepl("nytimes.com", harm_final_temp_kav$URL)] = "NY Times"
harm_final_temp_kav$Source[grepl("npr.org", harm_final_temp_kav$URL)] = "NPR"
harm_final_temp_kav$Source[grepl("slate.com", harm_final_temp_kav$URL)] = "Slate"
harm_final_temp_kav$Source[grepl("huffingtonpost.com", harm_final_temp_kav$URL)] = "Huffington Post"
harm_final_temp_kav$Source[grepl("politico.com", harm_final_temp_kav$URL)] = "Politico"
harm_final_temp_kav$Source[grepl("foxnews.com", harm_final_temp_kav$URL)] = "Fox"
harm_final_temp_kav$Source[grepl("breitbart.com", harm_final_temp_kav$URL)] = "Breitbart"
harm_final_temp_kav$Source[grepl("rushlimbaugh.com", harm_final_temp_kav$URL)] = "Rush Limbaugh"
harm_final_temp_kav$Source[grepl("theblaze.com", harm_final_temp_kav$URL)] = "The Blaze"
harm_final_temp_kav$Source[grepl("hannity.com", harm_final_temp_kav$URL)] = "Sean Hannity"
harm_model_kav = lme(MFDweight ~ lean, 
                 data = harm_final_temp_kav, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(harm_model_kav)
r.squaredGLMM(harm_model_kav)
```

@@

purity_final_temp_gs$Source[grepl("nytimes.com", purity_final_temp_gs$URL)] = "NY Times"
purity_final_temp_gs$Source[grepl("npr.org", purity_final_temp_gs$URL)] = "NPR"
purity_final_temp_gs$Source[grepl("slate.com", purity_final_temp_gs$URL)] = "Slate"
purity_final_temp_gs$Source[grepl("huffingtonpost.com", purity_final_temp_gs$URL)] = "Huffington Post"
purity_final_temp_gs$Source[grepl("politico.com", purity_final_temp_gs$URL)] = "Politico"
purity_final_temp_gs$Source[grepl("foxnews.com", purity_final_temp_gs$URL)] = "Fox"
purity_final_temp_gs$Source[grepl("breitbart.com", purity_final_temp_gs$URL)] = "Breitbart"
purity_final_temp_gs$Source[grepl("rushlimbaugh.com", purity_final_temp_gs$URL)] = "Rush Limbaugh"
purity_final_temp_gs$Source[grepl("theblaze.com", purity_final_temp_gs$URL)] = "The Blaze"
purity_final_temp_gs$Source[grepl("hannity.com", purity_final_temp_gs$URL)] = "Sean Hannity"
purity_model_gs = lme(MFDweight ~ lean, 
                 data = purity_final_temp_gs, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(purity_model_gs)
```

@@

```{r exp2_source_descriptives_kav, results = 'asis', echo = FALSE, message = F}
#Kav
final_kav$uniquewords = NA
final_kav$valenceavg = NA

@@

#change this to match
apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula.",
          caption = "Kavanaugh - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_Valence", "$SD_Valence$", "Number of Articles", "Total Words", "$M_Tokens$", "$SD_Tokens$", "$M_Types$", "SD_Types", "$M_Readability$", "$SD_Readability$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 6))
          )
```

```{r exp2_source_descriptives_gs, results = 'asis', echo = FALSE, message = F}
#Kav
#GS
final_gs$uniquewords = NA
final_gs$valenceavg = NA

@@

#calculate d
#harm
harm_d_kav = d.ind.t(m1 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T), 
                 m2 = mean(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
                 sd1 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"], na.rm = T),
                 sd2 = sd(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"], na.rm = T),
                 n1 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Conservative"]),
                 n2 = length(harm_final_temp_kav$MFDweight[harm_final_temp_kav$lean == "Liberal"]),
                 a = .05)

@@

#put in the numbers
tableprint_kav[1, ] = c("Harm/Care", harm_d_kav$M1, harm_d_kav$sd1, harm_d_kav$M2, harm_d_kav$sd1, 
                    summary(harm_model_kav)$tTable[2,4], summary(harm_model_kav)$tTable[2,5],
                    harm_d_kav$d)
tableprint_kav[2, ] = c("Fairness/Reciprocity", fair_d_kav$M1, fair_d_kav$sd1, fair_d_kav$M2, fair_d_kav$sd1, 
                    summary(fair_model_kav)$tTable[2,4], summary(fair_model_kav)$tTable[2,5],
                    fair_d_kav$d)
tableprint_kav[3, ] = c("Ingroup/Loyalty", ingroup_d_kav$M1, ingroup_d_kav$sd1, ingroup_d_kav$M2, ingroup_d_kav$sd1, 
                    summary(ingroup_model_kav)$tTable[2,4], summary(ingroup_model_kav)$tTable[2,5],
                    ingroup_d_kav$d)
tableprint_kav[4, ] = c("Authority/Respect", authority_d_kav$M1, authority_d_kav$sd1, authority_d_kav$M2, authority_d_kav$sd1, 
                    summary(authority_model_kav)$tTable[2,4], summary(authority_model_kav)$tTable[2,5],
                    authority_d_kav$d)
tableprint_kav[5, ] = c("Purity/Sanctity", purity_d_kav$M1, purity_d_kav$sd1, purity_d_kav$M2, purity_d_kav$sd1, 
                    summary(purity_model_kav)$tTable[2,4], summary(purity_model_kav)$tTable[2,5],
                    purity_d_kav$d)

@@

#calculate d
#harm
harm_d_gs = d.ind.t(m1 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T), 
                 m2 = mean(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
                 sd1 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"], na.rm = T),
                 sd2 = sd(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"], na.rm = T),
                 n1 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Conservative"]),
                 n2 = length(harm_final_temp_gs$MFDweight[harm_final_temp_gs$lean == "Liberal"]),
                 a = .05)

@@

#put in the numbers
tableprint_gs[1, ] = c("Harm/Care", harm_d_gs$M1, harm_d_gs$sd1, harm_d_gs$M2, harm_d_gs$sd1, 
                    summary(harm_model_gs)$tTable[2,4], summary(harm_model_gs)$tTable[2,5],
                    harm_d_gs$d)
tableprint_gs[2, ] = c("Fairness/Reciprocity", fair_d_gs$M1, fair_d_gs$sd1, fair_d_gs$M2, fair_d_gs$sd1, 
                    summary(fair_model_gs)$tTable[2,4], summary(fair_model_gs)$tTable[2,5],
                    fair_d_gs$d)
tableprint_gs[3, ] = c("Ingroup/Loyalty", ingroup_d_gs$M1, ingroup_d_gs$sd1, ingroup_d_gs$M2, ingroup_d_gs$sd1, 
                    summary(ingroup_model_gs)$tTable[2,4], summary(ingroup_model_gs)$tTable[2,5],
                    ingroup_d_gs$d)
tableprint_gs[4, ] = c("Authority/Respect", authority_d_gs$M1, authority_d_gs$sd1, authority_d_gs$M2, authority_d_gs$sd1, 
                    summary(authority_model_gs)$tTable[2,4], summary(authority_model_gs)$tTable[2,5],
                    authority_d_gs$d)
tableprint_gs[5, ] = c("Purity/Sanctity", purity_d_gs$M1, purity_d_gs$sd1, purity_d_gs$M2, purity_d_gs$sd1, 
                    summary(purity_model_gs)$tTable[2,4], summary(purity_model_gs)$tTable[2,5],
                    purity_d_gs$d)

@@

#tiff(filename = "exp2_graph_kav.tiff", res = 300, width = 4, 
#     height = 3, units = 'in', compression = "lzw")
#plot(graph_data_kav)
#dev.off()
```
